ShrinkNets: Learning Network Size while Training

### 2018-02-10 paper/ICML/impl.tex

\noindent\textbf{Preparing for Inference: } With ShrinkNets we obtain
reduced-sized networks during training, which is the first steps towards faster
inference. This networks are readily available for inference. However, because
they include switch layers---and therefore more parameters---they introduce
unnecessary overhead at inference time. To avoid this overhead, we reduce the
network parameters by combining each switch layer with its respective network
layer by multiplying the respective parameters before emitting the final trained
network. As a result, the final network is a dense network without any switching layers.

\noindent\textbf{Neural Garbage Collection: }ShrinkNets decides on-the-fly which
neurons to remove. Since ShrinkNets removes a large fraction of neurons, we must
dynamically resize the network at runtime to not unnecessarily impact network
training time. We implemented a neural garbage collection method as part of our
library which takes care of updating the necessary network layers as well as
updating optimizer state to reflect the neuron removal.

>>>>

\noindent\textbf{Preparing for Inference: } With \shrink we obtain
reduced-sized networks during training, which is the first steps towards faster
inference. This networks are readily available for inference. However, because
they include switch layers---and therefore more parameters---they introduce
unnecessary overhead at inference time. To avoid this overhead, we reduce the
network parameters by combining each switch layer with its respective network
layer by multiplying the respective parameters before emitting the final trained
network. As a result, the final network is a dense network without any switching layers.

\noindent\textbf{Neural Garbage Collection: } \shrink decides on-the-fly which
neurons to remove. Since \shrink removes a large fraction of neurons, we must
dynamically resize the network at runtime to not unnecessarily impact network
training time. We implemented a neural garbage collection method as part of our
library which takes care of updating the necessary network layers as well as
updating optimizer state to reflect the neuron removal.
